Viability of FTIR on fossil pollen

### 2020-02-21 manuscript.Rmd
started intro and methods

---
title: 'Viability of FTIR on fossil pollen'
author: 'Florian Muthreich'
date: '2020/02/04'
output:
  pdf_document: default
bibliography: references.bib
---

extracted fossil pollen from sediment.
ca 5 common taxa: Alnus, Picea, Pinus,

Research Questions:
1. chemical variation between taxa in the same cores.
2. chemical variation between taxa between cores 
3. chemical variation of pollen with depths/age
## Cores
Dalmuttlado:
- pine
- holocene

@@

>>>>

---
title: 'Viability of FTIR on fossil pollen'
author: 'Florian Muthreich'
date: '2020/02/04'
output:
  pdf_document: default
bibliography: references.bib
---
# Notes
extracted fossil pollen from sediment.
ca 5 common taxa: Alnus, Picea, Pinus,

## Cores
Dalmuttlado:
- pine
- holocene

@@

# Introduction
Research Questions:
1. chemical variation between taxa in the same cores.
2. chemical variation between taxa between cores 
3. chemical variation of pollen with depths/age

# Methods and Materials

Pollen extracted from sediment samples 
[@kampsAgentSeparationDissolved1985] SPT patent
[@nakagawaDensemediaSeparationMore1998] 
[@regnellPreparativeCentrifugationNew1996] density of pollen 1.4
